Topological Equivariant Artist Model for Visualization Library Architecture

### 2023-08-16 paper/main.tex
diagram figures + recreating data

For example, the disjoint union of two bundles, as shown in \autoref{fig:atct:local_trivalizations}, is the coproduct $\dbase^{a} \subseteq_{\dbase^{c}} \dbase^{b}$ over an overlap $\dbase^{c}$ and therefore the inclusion morphism must be commutative:
\begin{minipage}[c]{0.25\columnwidth} 
  \centering
  \begin{equation}
    \label{eq:atct:base_union}
  \begin{tikzcd}[row sep=large]
    \dbasec^{a}\sqcup_{\dbasec^{c}}\dbasec^{b} 
    & \dbasec_{b} \arrow[l, "\iota_b"', color=base] \\
    \dbasec_a \arrow[u, "\iota_a", color=base] 
    & \dbasec_c 
    \arrow[u, "\iota_c"', color=base] 
    \arrow[l, "\iota_c"', color=base] 
  \end{tikzcd}
\end{equation}
\end{minipage}

@@

\begin{minipage}[c]{.25\columnwidth}
\begin{tikzcd}
  \label{eq:atct:fiber_product}
  \dfiberc^{a}\times_{\dfiber^{c}} \dfiberc^{b} \arrow[d, "\pi_a"] \arrow[r, "\pi_b"] 
  & \dfiberc^{b} \arrow[d, "\pi_c"] 
  & {(temperature, time) \times_{time} (pressure, time)} \arrow[d, "\pi_a"] \arrow[r, "\pi_b"] 
  & {(pressure,time)} \arrow[d, "\pi_c"] \\
  \dfiberc^{a} \arrow[r, "\pi_c"] 
  & \dfiberc^{c}
  & {(temperature,time)} \arrow[r, "\pi_c"]
  & time
  \end{tikzcd}
\end{minipage}\hfill
\begin{minipage}[c]{.65\columnwidth}
  \note{will be little pictures like in 7 sketchs}
\end{minipage}

@@

\begin{figure}[H]
  \includegraphics*[width=1\columnwidth]{figures/tex/presheaf.pdf}
  \caption*{presheafs $\sheaf_1, sheaf_2$ mapping from intervals to the trignometric functions defined over those intervals }
\end{figure}

>>>>

For example, the disjoint union of two bundles, as shown in \autoref{fig:atct:local_trivalizations}, is the coproduct $\dbase^{a} \subseteq_{\dbase^{c}} \dbase^{b}$ over an overlap $\dbase^{c}$ and therefore the inclusion morphism must be commutative:
\begin{figure}
  \includegraphics*[width=1\columnwidth]{figures/tex/k_coproduct.pdf}
\end{figure}

@@

\begin{figure}
  \includegraphics*[width=1\columnwidth]{figures/tex/f_product.pdf}
\end{figure}

@@

\begin{figure}[H]
  \includegraphics*[width=1\columnwidth]{figures/tex/presheaf.pdf}
  \caption*{presheafs $\sheaf_1, \sheaf_2$ mapping from intervals to the trignometric functions defined over those intervals }
\end{figure}
